### 2022-10-21 manuscript/manuscript.tex
fixes

\begin{align}
  \label{eq:qterm}
  S_1 Q_t &= S_1 + S_2' + S_3' + \ldots + S_t' \\
  Q_t &= 1 + \sum_{i=1}^t \left((1-r)\kappa\right)^i
\end{align}

which converges to,

\begin{align}
  \label{eq:Qinf}
  Q_\infty &= \frac{1}{1-(1-r) \kappa}.
\end{align}

@@

where $L = n r_\text{BP}$ is the total segment length in Morgans. Let us define
the total asymptotic effect of associations from all sites as $Q_\infty^2$.
Then,

\begin{align}
  Q_\infty^2 &= \frac{2}{L}\int_0^{\nicefrac{n r_\text{BP}}{2}} Q_{\infty}(x)^2 dx  \\
  &=  \frac{2}{L} \int_0^{\nicefrac{L}{2}} \left(\frac{1}{1 - (1-x)Z}\right)^2 dx  \\
  &= \frac{2}{(1-Z) (2-(2-L) Z)}
\end{align}

@@

@@

>>>>

\begin{align}
  \label{eq:qterm}
  S_1 Q_t &= S_1 + S_2' + S_3' + \ldots + S_t' \\
  Q_t &= 1 + \sum_{i=1}^t (1-r)^i(1-\kappa)^i
\end{align}

or for continuous $t$,

\begin{align}
  \label{eq:q_t}
  Q_t &= 1+\frac{(1-\kappa) (1-r) \left(1-(1-\kappa)^T (1-r)^T\right)}{\kappa+(1-\kappa)r}
\end{align}

which as $T \to \infty$, converges to,

\begin{align}
  \label{eq:Qinf}
  Q_\infty &= \frac{1}{\kappa + r(1-\kappa)}.
\end{align}

@@

where $L = n r_\text{BP}$ is the total segment length in Morgans. Then, the
total asymptotic effect of associations from all sites as $Q_\infty^2$.  Then,

\begin{align}
  Q_\infty^2 &= \frac{2}{L}\int_0^{\nicefrac{L}{2}} Q_{\infty}(r)^2 dr  \\
  &=  \frac{2}{L} \int_0^{\nicefrac{L}{2}} \left(\frac{1}{1 - (1-r)Z}\right)^2 dr  \\
  &= \frac{2}{(1-Z) (2-(2-L) Z)}
\end{align}

@@

For the reasons described earlier, a single asymptotic $N_{e,\infty}$ cannot
fully characterize pairwise coalescent rates in all cases, and thus neutral
diversity levels depend on the full $N_{e,t}$, for which we integrate equation
\eqref{eq:q_t} to get,

\begin{align}
  \label{eq:net_integral}
  N_{e,t} \approx N \exp\left(-\frac{V_h}{L} \int_0^{\nicefrac{L}{2}} \left(1+\frac{(1-k) (1-r) \left(1-(1-k)^t (1-r)^t\right)}{k+(1-k)r} \right) dr \right).
\end{align}

@@

An analogous system can be found for $N_{e,t}$ using equation
\eqref{eq:net_integral}.
